Follow-up Samples

### 2017-01-11 submission/manuscript_outline_20161024.Rmd
add affiliations

Marc A Sze, Nielson T Baxter, Mack T Ruffin IV, Mary AM Rogers, and Patrick D Schloss${^\dagger}$

@@

Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
\end{center}

>>>>

Marc A Sze^1^, Nielson T Baxter^2^, Mack T Ruffin IV^3^, Mary AM Rogers^4^, and Patrick D Schloss^1^${^\dagger}$

@@

^1^Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
^2^Department of Internal Medicine, Division of Infectious Disease, University of Michigan, Ann Arbor, MI
^3^Department of Family Medicine and Community Medicine, Penn State Hershey Medical Center, Hershey, PA
^4^Department of Internal Medicine, University of Michigan, Ann Arbor, MI
\end{center}
